

% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)}
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject{Ethereum Project}{Spring, 2019}
\begin{itemize}
\item Utilized R to analyze the data of several tokens of Blockchain.
\item Determined the best fit distribution to the number of buys
and sells that a user makes.
\item Created layers of transactions of increasing amounts and then find the correlation between these layers and different features in the data.
\item Created a linear regression model to see if we can model price return based off of block chain features and purchase patterns.
\item Wrote a detailed report providing good visuals to explain each step in the solution.
\end{itemize}
\smallskip
\cvproject{Person Tracking}{Summer, 2017}
\begin{itemize}
\item Developed, modified and implemented robust object tracker by combining motion and appearance information to learn deep association metrics.
\end{itemize}
\smallskip
\cvproject{One Shot Learning}{Summer, 2017}
\begin{itemize}
\item One shot learning is the promising approach to learn good feature when little data is available.
\item Achieved 92\% accuracy on omniglot dataset using Siamese network with Bayesian optimization.
\end{itemize}
\smallskip
\cvproject{Automatic Defect Inspection of solar farm using drones}{Summer, 2017}
\begin{itemize}
\item Regular inspection of solar farm due to its wide size is strenuous.
\item Developed a model to classify and localize defect on thermal images captured by drones.
\end{itemize}
\smallskip
\cvproject{Anomaly detection using Auto-Encoders}{Summer, 2017}
\begin{itemize}
\item Developed a model to learn regular patterns from sensor data and detect unusual pattern.
\end{itemize}
\smallskip
\cvproject{Early Warning Fault Detection and Identification}{Summer, 2017}
\begin{itemize}
\item Developed an LSTM based model to forecast and detect outlier from sensor data.
\item Further, classified the given signal into one of the type of outlier.
\end{itemize}
\smallskip
\cvproject{Sentiment Analysis}{Summer, 2017}
\begin{itemize}
    \item Used bag-of-words, pre-trained Embedding and simple as well as bi-directional LSTM techniques for Sentiment Analysis.
\end{itemize}

\cvsection{ACTIVITIES}
